Efficient ancestry and mutation simulation with msprime 1.0

### 2021-09-20 paper.tex
Cite paper

An important goal of \msprime's development model is to maximise
accessibility for prospective users and contributors, and
to encourage diversity in our community.
Gender inequality is a major problem across
the sciences~\citep{shannon2019gender}
and in open source software development~\citep{trinkenreich2021women}.
Within our field, the contribution of women to early computational methods
in population genetics was marginalised~\citep{dung2019illuminating},
and women continue to be under-represented
in computational biology~\citep{bonham2017women}.
The authorship of our paper reflects these trends,
with a skew towards men and affiliations in the USA
and Europe. We know the importance of creating and strengthening networks to
develop and maintain a diverse community of contributors, and we are committed
to fostering a supportive and collaborative environment that helps to address these
inequalities in our field.

>>>>

An important goal of \msprime's development model is to maximise
accessibility for prospective users and contributors, and
to encourage diversity in our community.
Gender and racial inequality caused by discrimination and marginalisation
is a major problem across
the sciences~\citep{wellenreuther2016women,shannon2019gender}
and in open source software development~\citep{trinkenreich2021women}.
Within our field, the contribution of women to early computational methods
in population genetics was marginalised~\citep{dung2019illuminating},
and women continue to be under-represented
in computational biology~\citep{bonham2017women}.
The authorship of our paper reflects these trends,
with a skew towards men and affiliations in the USA
and Europe. We know the importance of creating and strengthening networks to
develop and maintain a diverse community of contributors, and we are committed
to fostering a supportive and collaborative environment that helps to address these
inequalities in our field.
